Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}

### 2014-12-18 Paper.tex
corrected refund from 150 to 100
refund gas.

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma}_1 & \text{if} \quad \mathbf{o} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
(\boldsymbol{\sigma}^{**}, g', \mathbf{s}, \mathbf{o}) & \equiv & \Xi(\boldsymbol{\sigma}_1, g, I) \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_d & \equiv & d \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_e & \equiv & e \\
\text{Let} \quad \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

@@

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{step}$ & 1 & Default amount of gas to pay for execution cycle. \\
$G_{balance}$ & 20 & Paid for a {\small BALANCE} operation. \\
$G_{stop}$ & 0 & Nothing paid for the {\small STOP} operation. \\
$G_{suicide}$ & 0 & Nothing paid for the {\small SUICIDE} operation. \\
$G_{sload}$ & 20 & Paid for a {\small SLOAD} operation. \\
$G_{sset}$ & 300 & Paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 100 & Paid for an {\small SSTORE} operation when the storage value's zeroness remains unchanged. \\
$G_{sclear}$ & 0 & Nothing paid for an {\small SSTORE} operation when the storage value is set to zero from non-zero. \\
$R_{sclear}$ & 150 & Refund given (added into refund counter) when the storage value is set to zero from non-zero. \\
$G_{create}$ & 100 & Paid for a {\small CREATE} operation. \\
$G_{createdata}$ & 5 & Paid per byte for a {\small CREATE} operation to succeed in placing code into state. \\
$G_{call}$ & 20 & Paid for a {\small CALL} operation. \\
$G_{exp}$ & 1 & Partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 1 & Partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 1 & Paid for every additional word when expanding memory. \\
$G_{txdatazero}$ & 1 & Paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 5 & Paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 500 & Paid for every transaction. \\
$G_{log}$ & 1 & Partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 1 & Paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 1 & Paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 10 & Paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 10 & Paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 1 & Partial payment for {\small *COPY} operations, multiplied by words copied, rounded up. \\

@@

As previously specified in section \ref{ch:model}, these definitions take place in the final context there. In particular we assume $O$ is the EVM state-progression function and define the terms pertaining to the next cycle's state $(\boldsymbol{\sigma}', \boldsymbol{\mu}')$ such that:

\begin{equation}
O(\boldsymbol{\sigma}, \boldsymbol{\mu}, A, I) \equiv (\boldsymbol{\sigma}', \boldsymbol{\mu}', A', I) \quad \text{with exceptions, as noted}
\end{equation}

>>>>

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma}_1 & \text{if} \quad \mathbf{o} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
(\boldsymbol{\sigma}^{**}, g', \mathbf{s}, \mathbf{o}) & \equiv & \begin{cases}
\Xi_{\mathtt{ECREC}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad a = 1 \\
\Xi_{\mathtt{SHA256}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad a = 2 \\
\Xi_{\mathtt{RIP160}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad a = 3 \\
\Xi(\boldsymbol{\sigma}_1, g, I) & \text{otherwise} \end{cases} \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_d & \equiv & d \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_e & \equiv & e \\
\text{Let} \; \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

As can be seen, there are three exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are three so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The three contracts in addresses 1, 2 and 3 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme and the RIPEMD 160-bit hash scheme respectively.

Their full formal definition is in Appendix \ref{app:precompiled}.

@@

\section{Precompiled Contracts}\label{app:precompiled}

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{step}$ & 1 & Default amount of gas to pay for execution cycle. \\
$G_{balance}$ & 20 & Paid for a {\small BALANCE} operation. \\
$G_{stop}$ & 0 & Nothing paid for the {\small STOP} operation. \\
$G_{suicide}$ & 0 & Nothing paid for the {\small SUICIDE} operation. \\
$G_{sload}$ & 20 & Paid for a {\small SLOAD} operation. \\
$G_{sset}$ & 300 & Paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 100 & Paid for an {\small SSTORE} operation when the storage value's zeroness remains unchanged. \\
$G_{sclear}$ & 0 & Nothing paid for an {\small SSTORE} operation when the storage value is set to zero from non-zero. \\
$R_{sclear}$ & 100 & Refund given (added into refund counter) when the storage value is set to zero from non-zero. \\
$G_{create}$ & 100 & Paid for a {\small CREATE} operation. \\
$G_{createdata}$ & 5 & Paid per byte for a {\small CREATE} operation to succeed in placing code into state. \\
$G_{call}$ & 20 & Paid for a {\small CALL} operation. \\
$G_{exp}$ & 1 & Partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 1 & Partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 1 & Paid for every additional word when expanding memory. \\
$G_{txdatazero}$ & 1 & Paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 5 & Paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 500 & Paid for every transaction. \\
$G_{log}$ & 1 & Partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 1 & Paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 1 & Paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 10 & Paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 10 & Paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 1 & Partial payment for {\small *COPY} operations, multiplied by words copied, rounded up. \\

@@

As previously specified in section \ref{ch:model}, these definitions take place in the final context there. In particular we assume $O$ is the EVM state-progression function and define the terms pertaining to the next cycle's state $(\boldsymbol{\sigma}', \boldsymbol{\mu}')$ such that:
\begin{equation}
O(\boldsymbol{\sigma}, \boldsymbol{\mu}, A, I) \equiv (\boldsymbol{\sigma}', \boldsymbol{\mu}', A', I) \quad \text{with exceptions, as noted}
\end{equation}
